Reproducible Validation and Replication Studies in Nanoscale Physics

### 2020-07-27 tex/ClementiBarba2020.tex
first bit of abstract

%%%% Abstract text to be placed here %%%%%%%%%%%%
\begin{abstract}
    The abstract text goes here. 
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%% Abstract text to be placed here %%%%%%%%%%%%
\begin{abstract}
    Credibility building activities in computational research include
    verification and validation, reproducibility and replication, and
    uncertainty quantification. Though orthogonal to each other, they are
    all related. This paper presents validation and replication studies in 
    electromagnetic excitation of nanoscale structures, where the quantity
    of interest is the wavelength at which resonance peaks occur. 
    The study uses the open-source software PyGBe: a boundary element
    solver with trecode acceleration and GPU capability.

    \end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
